Covariate analysis of CMC RNASeq data reprocessed with STAR-feature counts workflow with Ensembl v75 (ACC and DLPFC with CQN and SVA normlaisation)

### 2017-04-10 code/Rmd/CMC_ACC_DLPFC_STAR_ENSEMBL_v75_CQN_SVA.Rmd
Minor bug fix

### SVA
```{r sva}
# Get (null) design matrix
MODEL0 = DESIGN$design[,-grep('Dx.Tissue',colnames(DESIGN$design))] # Get null model by removing variable of interest
MODEL0 = MODEL0[,linColumnFinder(MODEL0)$indepCols]
MODEL1 = DESIGN$design
MODEL1 = MODEL1[,linColumnFinder(MODEL1)$indepCols]

@@

# Estimate surrogate variables
SURR.VAR = irwsva.build(CQN.GENE_EXPRESSION$y+CQN.GENE_EXPRESSION$offset,
                        MODEL1, MODEL0, n.sv = NUM.SV, B = 3, tol = 1e-22)$sv

@@

@@

# Store enrichment results
write.table(enrichment.results, file = 'CMC_ACC_DLPFC_EnrichResults.tsv', sep = '\t', row.names=F, quote=F)
ENRICH_OBJ = File('CMC_ACC_DLPFC_EnrichResults.tsv', 
                  name = 'Enrichment Analysis Results (Dx.Tissue)', 
                  parentId = CODE$properties$id)
annotations(ENRICH_OBJ) = annotations(CODE)
annotations(ENRICH_OBJ)$dataSubType = 'enrichResults'
ENRICH_OBJ = synStore(ENRICH_OBJ, activity = synGetActivity(COV_OBJ$properties$id))
stopCluster(cl)
```
|  *Results*                                  |  *SynapseID*                     |
|  -----------------------------------------  |   ---------                      |
|  Covariates                                 |  `r COV_OBJ$properties$id`       |
|  Counts (raw)                               |  `r COUNT_OBJ$properties$id`     |
|  Counts (lcpm)                              |  `r LCOUNT_OBJ$properties$id`    |
|  Offset (for gene length and gc content)    |  `r OFFSET_OBJ$properties$id`    |
|  Design Matrix                              |  `r DM_OBJ$properties$id`        |
|  Residual Expression (for eQTL analysis)    |  `r nEXP_OBJ$properties$id`      |
|  Differential Expression                    |  `r DEXP_OBJ$properties$id`      |
|  Enrichment Analysis                        |  `r ENRICH_OBJ$properties$id`    |

>>>>

### SVA
```{r sva}
# Get (null) design matrix
MODEL0 = DM1$design[,-grep('Dx.Tissue',colnames(DM1$design))] # Get null model by removing variable of interest
MODEL0 = MODEL0[,linColumnFinder(MODEL0)$indepCols]
MODEL1 = DM1$design
MODEL1 = MODEL1[,linColumnFinder(MODEL1)$indepCols]

@@

# Estimate surrogate variables
SURR.VAR = irwsva.build(CQN.GENE_EXPRESSION$y+CQN.GENE_EXPRESSION$offset,
                        MODEL1, MODEL0, n.sv = NUM.SV, B = 30, tol = 1e-22)$sv

@@

# Store surrogate variables
SURR.VAR %>%
  rownameToFirstColumn('SampleID') %>%
  write.table(file = 'CMC_ACC_DLPFC_SurrVar.tsv', sep = '\t', row.names=F, quote=F)
SURR.VAR_OBJ = File('CMC_ACC_DLPFC_SurrVar.tsv', name = 'Surrogate Variables', parentId = CODE$properties$id)
annotations(SURR.VAR_OBJ) = annotations(CODE)
annotations(SURR.VAR_OBJ)$dataSubType = 'SurrogateVariables'
SURR.VAR_OBJ = synStore(SURR.VAR_OBJ, activity = synGetActivity(COV_OBJ$properties$id))

@@

# Store enrichment results
write.table(enrichment.results, file = 'CMC_ACC_DLPFC_EnrichResults.tsv', sep = '\t', row.names=F, quote=F)
ENRICH_OBJ = File('CMC_ACC_DLPFC_EnrichResults.tsv', 
                  name = 'Enrichment Analysis Results (Dx.Tissue)', 
                  parentId = CODE$properties$id)
annotations(ENRICH_OBJ) = annotations(CODE)
annotations(ENRICH_OBJ)$dataSubType = 'enrichResults'
ENRICH_OBJ = synStore(ENRICH_OBJ, activity = synGetActivity(COV_OBJ$properties$id))
stopCluster(cl)
```
|  *Results*                                  |  *SynapseID*                     |
|  -----------------------------------------  |   ---------                      |
|  Covariates                                 |  `r COV_OBJ$properties$id`       |
|  Counts (raw)                               |  `r COUNT_OBJ$properties$id`     |
|  Counts (lcpm)                              |  `r LCOUNT_OBJ$properties$id`    |
|  Offset (for gene length and gc content)    |  `r OFFSET_OBJ$properties$id`    |
|  Design Matrix                              |  `r DM_OBJ$properties$id`        |
|  Surrogate Variables                        |  `r SURR.VAR_OBJ$properties$id`  |
|  Residual Expression (for eQTL analysis)    |  `r nEXP_OBJ$properties$id`      |
|  Differential Expression                    |  `r DEXP_OBJ$properties$id`      |
|  Enrichment Analysis                        |  `r ENRICH_OBJ$properties$id`    |
